Experimental and numerical studies of the effects of resonant and random excitations of the proton beam in the LHC, with applications to the design of a pulsed hollow electron lens for active halo control

### 2018-02-19 resex.tex
Revised Section II A on HEL

\begin{table}
  \caption{HL-LHC design parameters at top energy~\cite{hlcdr} and
    parameters relevant to the HEL. Optics parameters at the HEL are
    based on a position of $-$40~m for Beam~1 (B1) and $+$40~m for
    Beam~2 (B2) from the interaction point IP4, using HL-LHC optics
    V1.3 with $\beta^{*} = \q{0.15}{m}$~\cite{hlv13}.}
  \label{tab:hllhc_param}
  \begin{ruledtabular}
    \begin{tabular}{lccc}
      Beam parameters & Value(B1) & Value(B2) & Unit\\
      \colrule
      Beam energy  $E_{p}$  &  \multicolumn{2}{c}{7} & TeV\\
      Number of bunches $n_b$ & \multicolumn{2}{c}{2748} & - \\
      Number of particles per bunch $N_b$ & \multicolumn{2}{c}{$2.2\times 10^{11}$} & -\\
      Normalized emittance $\epsilon_{N,x/y}$ & \multicolumn{2}{c}{2.5} & $\mu$m\\
      Bunch spacing & \multicolumn{2}{c}{25} & ns\\
      \colrule
      \multicolumn{4}{l}{Optics paramters at HEL (Beam~1) \footnote{As the Twiss parameters at IP4 do not change during the entire squeeze, and IP4 and the HEL are only separated by a drift space, the Twiss parameters stay constant also at the HEL during the entire squeeze.}} \\
      \colrule
      $\beta_{x}$ at HEL  & 197.5 & 280.6 & m\\
      $\beta_{y}$ at HEL & 211.9 & 262.6 m\\
      Dispersion $D_{x}$ at HEL & 0.0& 0.0 & m\\
      Dispersion $D_{y}$ at HEL & 0.0& 0.0 & m\\
      Proton beam size $\sigma_{p,x}$ at HEL & 0.26 & 0.31& mm \\		
      Proton beam size $\sigma_{p,y}$ at HEL & 0.27 & 0.30 &mm \\
      \multicolumn{4}{l}{scraping position}\\ \hspace{1cm}$\sigma_{p}=\max(\sigma_{p,x},\sigma_{p,y})$ & 0.27& 0.31 & mm\\
    \end{tabular}
  \end{ruledtabular}
\end{table}

\begin{table}
  \caption{HL-LHC hollow electron lens parameters as defined in
    Ref.~\cite{hel_cdr}.}
  \label{tab:hel_param}
  \begin{ruledtabular}
    \begin{tabular}{lcc}
      Geometry & Value& Unit\\
      \colrule
      Length $L$    &  3 & m\\
      % 3-8 sigmap with 3.5 um -> 3.55-9.47 for 2.5 um emittance
      Desired range of scraping positions & 3.5-9.5 &$\sigma_p$\\
      \colrule
      Magnetic fields & & \\
      \colrule
      Gun solenoid, $B_g$ & 0.2-0.4 & T\\
      Main solenoid, $B_m$ & 2-6 & T\\
      Collector solenoid, $B_c$ & 0.2-0.4 & T\\
      Compression factor ($k=\sqrt{B_m/B_g}$) & 2.2-5.5 & -\\
      \colrule
      Electron gun & & \\
      \colrule
      Peak yield $I_e$ at 10~keV & 5.0 & A\\
      Gun perveance $P$ & 5 & $\mu$perv\\
      Inner/outer cathode radius, $R_1/R_2$ & 6.75/12.7 & mm\\
      \colrule
      High voltage modulator & & \\
      \colrule
      Cathode-anode voltage & 10.0 & kV\\
      Rise time (10\%-90\%) & 200 & ns \\
      Repetition rate & 35 & kHz
    \end{tabular}
  \end{ruledtabular}
\end{table}

>>>>

\begin{table}
  \caption{HL-LHC design parameters at top energy~\cite{hlcdr} and
    parameters relevant to the HEL. Optics parameters at the HEL are
    based on a position of $-$40~m for Beam~1 (B1) and $+$40~m for
    Beam~2 (B2) from the interaction point IP4, using HL-LHC optics
    V1.3 with $\beta^{*} = \q{0.15}{m}$~\cite{hlv13}.}
  \label{tab:hllhc_param}
  \begin{ruledtabular}
    \begin{tabular}{lccc}
      Beam parameters & \multicolumn{2}{c}{Value} & Unit\\
                       & B1 & B2 & \\
      \colrule
      Beam energy,  $E_{p}$  &  \multicolumn{2}{c}{7} & TeV\\
      Number of bunches, $n_b$ & \multicolumn{2}{c}{2748} &  \\
      Bunch population, $N_b$ & \multicolumn{2}{c}{$2.2\times 10^{11}$} & \\
      Normalized emittance, $\epsilon_{N,x/y}$ & \multicolumn{2}{c}{2.5} & $\mu$m\\
      Bunch spacing & \multicolumn{2}{c}{25} & ns\\
      \colrule
      \multicolumn{4}{l}{Optics parameters at HEL (B1)\footnote{As the
      Twiss parameters at IP4 do not change during the entire squeeze
      of the optical functions, and IP4 and the HEL are only separated
      by a drift space, the Twiss parameters stay constant also at the
      HEL during the squeeze.}} \\
      \colrule
      $\beta_{x}$ at HEL  & 197.5 & 280.6 & m\\
      $\beta_{y}$ at HEL & 211.9 & 262.6 & m\\
      Dispersion $D_{x}$ at HEL & 0.0& 0.0 & m\\
      Dispersion $D_{y}$ at HEL & 0.0& 0.0 & m\\
      Proton beam size $\sigma_{p,x}$ at HEL & 0.26 & 0.31& mm \\		
      Proton beam size $\sigma_{p,y}$ at HEL & 0.27 & 0.30 &mm \\
      \multicolumn{4}{l}{Scale of scraping positions}\\ \hspace{6ex}$\sigma_{p}=\max(\sigma_{p,x},\sigma_{p,y})$ & 0.27& 0.31 & mm\\
    \end{tabular}
  \end{ruledtabular}
\end{table}

\begin{table}
  \caption{HL-LHC hollow electron lens parameters, as defined in
    Ref.~\cite{hel_cdr}.}
  \label{tab:hel_param}
  \begin{ruledtabular}
    \begin{tabular}{lcc}
      Geometry & Value& Unit\\
      \colrule
      Length, $L$    &  3 & m\\
      % 3-8 sigmap with 3.5 um -> 3.55-9.47 for 2.5 um emittance
      Desired range of scraping positions & 3.5--9.5 &$\sigma_p$\\
      \colrule
      Magnetic fields & & \\
      \colrule
      Gun solenoid, $B_g$ & 0.2--0.4 & T\\
      Main solenoid, $B_m$ & 2--6 & T\\
      Collector solenoid, $B_c$ & 0.2--0.4 & T\\
      Compression factor, $k \equiv \sqrt{B_m/B_g}$ & 2.2--5.5 &  \\
      \colrule
      Electron gun & & \\
      \colrule
      Peak yield $I_e$ at 10~keV & 5.0 & A\\
      Gun perveance, $P$ & 5 & $\mu$perv\\
      Inner/outer cathode radii, $R_1/R_2$ & 6.75/12.7 & mm\\
      \colrule
      High-voltage modulator & & \\
      \colrule
      Cathode-anode voltage & 10.0 & kV\\
      Rise time (10\%-90\%) & 200 & ns \\
      Repetition rate & 35 & kHz
    \end{tabular}
  \end{ruledtabular}
\end{table}
